### 2019-08-04 Thesis/conc.tex
Added some more pages to the introduction.
Put everything into one document, added title page, did spell check etc.

\documentclass[11pt]{report}

\let\FEWFONTS=1
\input{../common/preamble}

\begin{document}

\chapter{Further Directions}

@@

For example, fix $X\in\{\bB,\bN\}$ and let \emph{Nondeterministic PCF} be the langauge PCF, together with a constant $\ask_X \from \bool$ that plays the role of a nondeterministic oracle.  

@@

  \caption{Big-step operational semantics for Nondeterministic PCF with may testing}

@@

There is a surprising and elegant definition of nondeterministic innocence (see Levy \cite{levy2014morphisms}, with the correction given by Tsukada and Ong in \cite[Proposition 46]{TsukadaSheaves}), which we shall not detail here.
Tsukada and Ong have also demonstrated that it is instructive to consider strategies as presheaves over plays, where we assign to each individual play a set of possible branches that lead us to that play.  
In this formalism, the innocent nondeterministic strategies are preciesly those presheaves that are sheaves with respect to a certain natural Grothendieck topology.

@@

It is worth mentioning that although we can prove computational adequacy for our various Kleisli categories (and categories of the form $\G/\X$), it does not automatically follow that we can prove adequacy in the same way for the various quotiented categories.  
An important example is our model of countable nondeterminism with must testing.  
It is well known (see, e.g., \cite{Apt,PlotkinApt}) that countable nondeterminism is inextricably linked to dicontinuity of composition, which robs us of an important ingredient in the standard order-theoretic proof of adequacy.

@@

\bibliographystyle{alpha2}
\bibliography{../common/phd_bibliography}

\end{document}

>>>>

\chapter{Further Directions}
\label{ChapFurtherDirections}

@@

For example, fix $X\in\{\bB,\bN\}$ and let \emph{Nondeterministic PCF} be the language PCF, together with a constant $\ask_X \from \bool$ that plays the role of a nondeterministic oracle.  

@@

  \caption{Big-step operational semantics for Nondeterministic PCF and may testing}

@@

There is a surprising and elegant definition of nondeterministic innocence (see Levy \cite{levy2014morphisms}, with the correction given by Tsukada and Ong in \cite[Proposition 46]{TsukadaSheaves}), which we shall not detail here.
Tsukada and Ong have also demonstrated that it is instructive to consider strategies as presheaves over plays, where we assign to each individual play a set of possible branches that lead us to that play.  
In this formalism, the innocent nondeterministic strategies are precisely those presheaves that are sheaves with respect to a certain natural Grothendieck topology.

@@

It is worth mentioning that although we can prove computational adequacy for our various Kleisli categories (and categories of the form $\G/\X$), it does not automatically follow that we can prove adequacy in the same way for the various quotiented categories.  
An important example is our model of countable nondeterminism with must testing.  
It is well known (see, e.g., \cite{Apt,PlotkinApt}) that countable nondeterminism is inextricably linked to discontinuity of composition, which robs us of an important ingredient in the standard order-theoretic proof of adequacy.

@@
